Optimal Transport Problems

### 2018-03-24 reports/progress-report/progress.tex
add cite

\documentclass[11pt]{amsart}
\usepackage{../am221}
\linespread{1.2}
\title{Optimal Transport Problems}
\renewcommand{\b}{\mathbf}
\newcommand{\R}{\mathbb{R}}
\usepackage{bbm}
\newcommand{\one}{\mathbbm{1}}
\newcommand{\E}{\mathbb{E}}
\author{Jiafeng Chen\and Francisco Rivera}
\date{\today}

\theoremstyle{remark}
\newtheorem{rmk}{Remark}
\begin{document}
    \maketitle
    \section{Theoretical foundations} 
    Let $\b a \in \R^m_{\ge 0}$ and $\b b \in \R^n_{\ge 0}$ be two vectors of
    nonnegative real numbers such that $\b a^T \one = \b b^T \one = 1$, where
    $a_i$ and $b_j$ represents the amount of ``mass'' at different positions. 
    We are
    interested in a matrix $\b P \in \R^{m \times n}_{\ge 0}$ where $P_{ij}$
    prescribes
    the amount of mass flowing from $a_i$ to $b_j$. Naturally, we must have
    $\sum_j P_{ij} = a_i$ and $\sum_i P_{ij} = b_j$, so that mass is preserved.
    Let $\b C
    \in \R^{m\times n}$ be a \emph{cost matrix}, where $C_{ij}$ represents the
    cost of transporting one unit of $a_i$ to $b_j$. The \emph{Kantorovich
    optimal transport problem} is the following linear program: \begin{align*}
    \min_{\b P \in  \R^{m \times n}_{\ge 0}} \, & \sum_{i,j} P_{ij} C_{ij} \\
    \text{subjected to } & \b P \one = \b a \\
    & \b P^T \one = \b b
    \end{align*}

@@

\end{document}

>>>>

\documentclass[11pt]{amsart}
\usepackage{../am221}
\linespread{1.2}
\title{Optimal Transport Problems}
\newcommand{\R}{\mathbb{R}}
\usepackage{bbm}
\newcommand{\one}{\mathbbm{1}}
\newcommand{\E}{\mathbb{E}}
\usepackage{cleveref}
\author{Jiafeng Chen\and Francisco Rivera}
\date{\today}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=Blue, linkcolor=blue}
\renewcommand{\b}{\mathbf}

\theoremstyle{remark}
\newtheorem{rmk}{Remark}
\begin{document}
    \maketitle
    \section{Theoretical foundations}
    The following is a concise review of Chapters 2 and 3 in 
    \cite{peyre2017computational}.

    Let $\b a \in \R^m_{\ge 0}$ and $\b b \in \R^n_{\ge 0}$ be two vectors of
    nonnegative real numbers such that $\b a^T \one = \b b^T \one = 1$, where
    $a_i$ and $b_j$ represents the amount of ``mass'' at different positions. 
    We are
    interested in a matrix $\b P \in \R^{m \times n}_{\ge 0}$ where $P_{ij}$
    prescribes
    the amount of mass flowing from $a_i$ to $b_j$. Naturally, we must have
    $\sum_j P_{ij} = a_i$ and $\sum_i P_{ij} = b_j$, so that mass is preserved.
    Let $\b C
    \in \R^{m\times n}$ be a \emph{cost matrix}, where $C_{ij}$ represents the
    cost of transporting one unit of $a_i$ to $b_j$. The \emph{Kantorovich
    optimal transport problem} is the following linear program: \begin{align*}
    \min_{\b P \in  \R^{m \times n}_{\ge 0}} \, & \sum_{i,j} P_{ij} C_{ij} \\
    \text{subjected to } & \b P \one = \b a \\
    & \b P^T \one = \b b
    \end{align*}

@@

\bibliographystyle{alpha}
\bibliography{../optimal-transport}
\end{document}
